Case Study: Gene Set Enrichment Analysis (Human Data Set)

### 2018-08-29 datasets/GSEA/fgsea-human.Rmd
Change code chunk label in gsea

```{r goseq, message=FALSE}
if (!file.exists(goset_file)) {
    mart <- useMart("ensembl", "hsapiens_gene_ensembl")
    goSets <- getBM(c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar( goSets$go_id ) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    saveRDS(goSets, file = goset_file)
} else {
    goSets <- readRDS(goset_file)
}
```

>>>>

```{r gocat, message=FALSE}
if (!file.exists(goset_file)) {
    mart <- useMart("ensembl", "hsapiens_gene_ensembl")
    goSets <- getBM(c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar( goSets$go_id ) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    saveRDS(goSets, file = goset_file)
} else {
    goSets <- readRDS(goset_file)
}
```
